Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-11 papers/marlowe2019/paper.tex
fix image spacing
Rephraze a few things. Removed empty input example

In order to spend an existing transaction output protected by a \emph{Validator},
one must create a transaction (a \emph{PendingTx}) that has an \emph{input} that references the transaction output,
and contains a \emph{Redeemer}, such that \texttt{Validator(Data Script, Redeemer, PendingTx)} evaluates to $True$.
In order to spend a transaction output protected by a \emph{public key}, one must provide a valid signature
made with the private key corresponding to the transaction public key.

@@

\noindent
where \texttt{accounts} maps account ids to their balances, \texttt{choices} stores user made choice values,
\texttt{boundValues} stores evalutated \texttt{Value}'s introduced by \texttt{Let} expressions,
and \texttt{minSlot} holds a minimal slot number that a contract has seen, to avoid `time travel to the past'.

@@

\begin{verbatim}
data TransactionInput = TransactionInput
    { txInterval :: SlotInterval
    , txInputs   :: [Input] }

data TransactionOutput =
    TransactionOutput
        { txOutWarnings :: [TransactionWarning]
        , txOutPayments :: [Payment]
        , txOutState    :: State
        , txOutContract :: Contract }
    | Error TransactionError

computeTransaction :: TransactionInput -> State -> Contract -> TransactionOutput
\end{verbatim}

\noindent
The interpreter reduces a contract until it becomes quiescent: either it evaluates to \texttt{Close},
or it expects a user input in a \texttt{When} construct.
All \texttt{Pay, If, Let, Close} constructs are evaluated immediately.

@@

Sometimes it is necessary to just evaluate a contract in a given moment in time,
without providing any inputs. Consider the following example:

\begin{verbatim}
If (SlotIntervalStart `ValueGT' 100)
    When [] (Slot 200)
        (Pay aliceAccount (Party bobPubKey) (Constant 1000))
    Close
\end{verbatim}

Let us say that Alice has 1000 Lovelace on her account, and Bob wants to receive the payment.
The payment could be obtained only after \texttt{When} has timed out after slot 200.
But if we evaluate the contract after slot 200, \texttt{If} reduces to \texttt{Close}, and
Bob will not receive the payment. So he must evaluate the contract before slot 100 to
reduce \texttt{If} to \texttt{When}.
To achieve that, Bob must spend the contract transaction output with an empty list of inputs in the \emph{Redeemer}.
He can then do the same after slot 200 to receive the payment.

@@

\begin{wrapfigure}[6]{l}{0.25\textwidth}
    \vspace*{-0.3in}
    \includegraphics[scale=0.2]{hole_options_2.png}
\end{wrapfigure}
A complete contract can be written in this guided way with the user needing only to fill in strings and numbers by hand. This approach to writing holes in your code and ``asking'' the compiler what you could put in there is easy to implement in a DSL because there are very limited options, however is is also becoming popular with more complex languages such as Haskell and Idris.

>>>>

In order to spend an existing transaction output protected by a \emph{Validator},
one must create a transaction (a \emph{PendingTx}) that has an \emph{input} that references the transaction output,
and contains a \emph{Redeemer}, such that \texttt{Validator(Data Script, Redeemer, PendingTx)} evaluates to $True$.
A valid signature is required to spend a \emph{public key} transaction output.

@@

\noindent
where \texttt{accounts} maps account ids to their balances, \texttt{choices} stores user made choice values,
\texttt{boundValues} stores evaluated \texttt{Value}'s introduced by \texttt{Let} expressions,
and \texttt{minSlot} holds a minimal slot number that a contract has seen, to avoid `time travel to the past'.

@@

\begin{verbatim}
computeTransaction :: TransactionInput -> State -> Contract -> TransactionOutput

data TransactionInput = TransactionInput
    { txInterval :: SlotInterval
    , txInputs   :: [Input] }

data TransactionOutput =
    TransactionOutput
        { txOutWarnings :: [TransactionWarning]
        , txOutPayments :: [Payment]
        , txOutState    :: State
        , txOutContract :: Contract }
    | Error TransactionError
\end{verbatim}

\noindent
Given a list of \texttt{Input}'s from \emph{Redeemer}, the interpreter reduces a contract until it becomes quiescent: either it evaluates to \texttt{Close},
or it expects a user input in a \texttt{When} construct.
All \texttt{Pay, If, Let, Close} constructs are evaluated immediately.

@@

@@

\begin{wrapfigure}[6]{l}{0.25\textwidth}
    \vspace*{-0in}
    \includegraphics[scale=0.2]{hole_options_2.png}
\end{wrapfigure}
A complete contract can be written in this guided way with the user needing only to fill in strings and numbers by hand. This approach to writing holes in your code and ``asking'' the compiler what you could put in there is easy to implement in a DSL because there are very limited options, however is is also becoming popular with more complex languages such as Haskell and Idris.
